---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cofeatureR

cofeatureR is an R Package that provides functions for plotting cofeature matrices (aka. sample-feature matrices). For example:

```{r example, dev = "svg", echo = FALSE, message = FALSE}
library("cofeatureR")
v1 <- c("RCOR1", "NCOR1", "LCOR", "RCOR1", "RCOR1", "RCOR1", "RCOR1")
v2 <- c("sampleA", "sampleC", "sampleB", "sampleC", "sampleA", "sampleC", "sampleC")
v3 <- c("Deletion", "Deletion", "SNV", "Rearrangement", "SNV", "Rearrangement", "SNV")
feature.order <- c("RCOR1", "NCOR1", "LCOR")
sample.id.order <- c("sampleA", "sampleB", "sampleC")
in.df <- dplyr::data_frame(feature = v1, sampleID = v2, type = v3)
fill.colors <- c("Deletion" = "Blue", "Rearrangement" = "Green", "SNV" = "Red")
 
plot_cofeature_mat(in.df)
```

Some features include:

* Multiple types can be specified for a sample-feature
* Custom colors for each type
* Custom ordering of features and samples

# Installation

To get the released version from CRAN:

```{r, eval = FALSE}
install.packages("cofeatureR")
```

To install the latest developmental version from github:

```{r, eval = FALSE}
devtools::install_github("tinyheero/tinyutils")
```
